A Comparative study of Dask and Spark for neuroimaging pipelines

### 2019-07-02 latex/paper.tex
Comments and fixes on III.A

We varied four parameters in our experiments, as shown in
Table~\ref{tab:param}. We varied (1) the number of workers to assess the
scalability of the engines, (2) the number of BigBrain blocks in
Incrementation and Histogram to measure the effect of different IO patterns
and parallelization degrees, and (3) the number of iterations and sleep
delay in Incrementation to evaluate the effect of job length.
We run the experiments in a non-deterministic order and clear the cache of each
worker before each benchmark.

@@

%%% INCREMENTATION %%%
%% worker
\subsection{Incrementation: Number of workers}
Figure~\ref{fig:inc_ms_worker} shows the makespan for the incrementation algorithm on
the y-axis and the number of workers on the x-axis; the color represents the
different frameworks. Overall, there is no substantial makespan difference between
the frameworks. Also, the increase in performance is not proportional to the number
of workers; performance even decreases when we reach 8 workers.

In Figure~\ref{fig:inc_tt_worker}, the y-axis shows the total execution time of the
incrementation application. The hatch indicates the total time spent for: read,
compute, write, and overhead. Again, the color represents the frameworks. The
computing time stays similar when the number of workers increases. However, the IO
time and overhead increase proportionally to the number of workers.

\begin{figure}[!b]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_worker.png}%
        \caption{Incrementation makespan}\label{fig:inc_ms_worker}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_idle_worker.png}%
        \caption{Incrementation total time}\label{fig:inc_tt_worker}
    \end{subfigure}
    \caption{125 blocks, 10 iterations, 4 sec.\ sleep delay}\label{fig:inc_worker}
\end{figure}

% blocks
\subsection{Incrementation: Number of blocks}
In Figure~\ref{fig:inc_block}, Spark is not compared for 30 blocks. This is because
Spark has a 2GB limitation in the task size it can compute.

The Figure~\ref{fig:inc_ms_block} shows the makespan evolution when varying the
number of blocks. The compute time increase when there are more blocks. This is
because the sleep delay is constant throughout this experiment and there are more
compute tasks when the number of blocks increases.

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_block.png}%
        \caption{Incrementation makespan}\label{fig:inc_ms_block}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_idle_block.png}%
        \caption{Incrementation total time}\label{fig:inc_tt_block}
    \end{subfigure}
    \caption{10 iterations, 4 sec.\ sleep delay, 8 instances}\label{fig:inc_block}
\end{figure}

@@

%%%%% DISCUSSION %%%%%
\section{Discussion}
\subsection{IO Time}

>>>>

We varied four parameters in our experiments, as shown in
Table~\ref{tab:param}. We varied (1) the number of workers to assess the
scalability of the engines, (2) the number of BigBrain blocks in
Incrementation and Histogram to measure the effect of different IO patterns
and parallelization degrees, and (3) the number of iterations and sleep
delay in Incrementation to evaluate the effect of job length.
It should be noted that increasing the number of blocks or iterations also
increases the total compute time of the application for a given sleep
delay. To avoid any potential external bias such as background load on the
network, we ran the experiments in a randomized order and cleared the page
cache of each worker before each execution.

@@

%%% INCREMENTATION %%%
%% worker
\subsection{Incrementation: Number of workers}
Figure~\ref{fig:inc_ms_worker} shows the makespan of the Incrementation
application for different numbers of workers and for different engines.
Overall, there is no substantial makespan difference between the engines.
Dask seems to have a slight advantage over Spark, \TG{X (toutes les Dask vs Spark)} seconds on
average, with Delayed and Futures being slightly better than Bags.

For all engines, the makespan is far from decreasing linearly with the
number of workers. Note that there are 8 threads per worker. The makespan
even increases between 4 and 8 workers. This is due to the high impact of
data transfers and engine overhead on the application.

Figure~\ref{fig:inc_tt_worker} shows the total execution time of the
Incrementation application, broken down into data transfer (read and
write), compute (sleep), and overhead time. As expected, the computing time
stays similar when the number of workers increases. However, the data
transfer time and overhead increase proportionally to the number of
workers \TG{check if indeed proprotional, add regression slopes}.

On Figure~\ref{fig:inc_tt_worker}, we also note that Spark's overhead is
slightly lower than Dask's in particular as the number of workers increase.
Within Dask, Delayed and Futures have a higher overhead than Bags. However,
overhead differences are compensated by an increase of data transfer time,
as a reduced overhead increases the concurrency between data transfers.

\begin{figure}[!b]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_worker.png}%
        \caption{Incrementation makespan}\label{fig:inc_ms_worker}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_idle_worker.png}%
        \caption{Incrementation total time}\label{fig:inc_tt_worker}
    \end{subfigure}
    \caption{125 blocks, 10 iterations, 4-s delay, 8 threads/worker}\label{fig:inc_worker}
\end{figure}

% blocks
\subsection{Incrementation: Number of blocks}

Figure~\ref{fig:inc_ms_block} shows the Incrementation makespan when
varying the number of image blocks for a constant BigBrain image size. We
were not able to run Spark for 30 blocks due to its 2GB limitation in the
task size it can compute. Once again, we do not observe any significant
difference among the engines.

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_block.png}%
        \caption{Incrementation makespan}\label{fig:inc_ms_block}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_idle_block.png}%
        \caption{Incrementation total time}\label{fig:inc_tt_block}
    \end{subfigure}
    \caption{10 iterations, 4-s delay, 8 workers, 8 threads/worker}\label{fig:inc_block}
\end{figure}

@@

%%%%% DISCUSSION %%%%%
\section{Discussion}

\TG{Talk about engine overhead: (1) where is it coming from? (2) 
explain the impact on data transfers with a graph.}

\subsection{IO Time}
